Plot responses to model covariates to inform threshold choices for VOCC

### 2019-08-14 analysis/VOCC/3-variable-response-plots.Rmd
calculate optimal values for enviro variables

Species
```{r}
#species <- params$species
# # Species run so far...
species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

Dissolved O2 plots
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
# covariates <- ""

@@

model_list <- list(
  adult_survey_all=adult_survey_all, imm_survey_all=imm_survey_all,
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

```{r}
d <- list()
do_plots <- list()
for (i in seq_len(length(model_list))) {
  d[[i]] <- time_varying_density(model_list[[i]], predictor = "do_mlpl")
  do_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Dissolved O2", xlimits = c(0,8)) + ggtitle(paste(species, names(model_list[i])))
}
print(do_plots)
```

Temperature plots
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

@@

```{r}
d <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  d[[i]] <- time_varying_density(temp_model_list[[i]], predictor = "temp")
  #d[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")
  temp_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Temperature", xlimits = c(2,10)) +
    ggtitle(paste(species,names(temp_model_list[i])))
}
print(temp_plots)
```

@@

Depth plots
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

@@

```{r}
d <- list()
depth_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  d[[i]] <- time_varying_density(depth_model_list[[i]], predictor = "depth")
  d[[i]]$x <- exp(d[[i]]$x)
  depth_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Depth", xlimits = c(0,1000)) + 
    ggtitle(paste(species, names(depth_model_list[i])))
}
print(depth_plots)
```

```{r}
png(
  file = paste0("figs/", spp, 
    "/depth-", spp, covs, "-priors-", priors, ".png"), 
  res = 600,
  units = "in",
  width = 8.5, 
  height = 11
)
gridExtra::grid.arrange(
  grobs = depth_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Plot time-varying effect of trawling at mean depth
```{r}
trawl_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  r <- depth_model_list[[i]]$tmb_obj$report()
  b3 <- r$b_rw_t[, 3]
  yrs <- sort(unique(depth_model_list[[i]]$data$year))
  b_j <- depth_model_list[[i]]$model$par[1:length(yrs)]

  SE <- 0.35 #Place-holder

@@

```

>>>>

Species
```{r}
# species <- params$species
# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
 species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

@@

Load Dissolved O2 models
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
# covariates <- ""

@@

model_list <- list(
  adult_survey_all = adult_survey_all, imm_survey_all = imm_survey_all,
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

Load temperature models
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

@@

Save optimal values

```{r}
td <- list()

for (i in seq_len(length(temp_model_list))) {
  td[[i]] <- time_varying_density(temp_model_list[[i]], predictor = "temp")
  #browser()
  if (length(td[[i]])>0) td[[i]]$model <- names(temp_model_list[i])
}

tdat <- do.call("rbind", td)

tdat <- tdat %>%
  group_by(model) %>%
  mutate(maxy = max(y_hat)) %>%
  ungroup() %>%
  mutate(meanymax = mean(maxy), sdymax = sd(maxy)) %>%
  filter(maxy < (meanymax + 2 * sdymax))

hist(tdat$maxy)

optimal_temp <- get_optimal_value(tdat, xlimits = c(3, 8))

do <- list()

for (i in seq_len(length(model_list))) {
 do[[i]] <- time_varying_density(model_list[[i]], predictor = "do_mlpl")
 if (length(do[[i]])>0) do[[i]]$model <- names(model_list[i])
}
odat <- do.call("rbind", do)

odat <- odat %>%
  group_by(model) %>%
  mutate(maxy = max(y_hat)) %>%
  ungroup() %>%
  mutate(meanymax = mean(maxy), sdymax = sd(maxy)) %>%
  filter(maxy < (meanymax + 2 * sdymax))

hist(odat$maxy)

optimal_do <- get_optimal_value(odat, xlimits = c(0.5, 6))

date <- Sys.time()

params <- data.frame(species, optimal_do, optimal_temp, date)

other_params <- readRDS(paste0("data/optimal-values-by-species.rds"))
params <- rbind(other_params, params)
saveRDS(params, file = "data/optimal-values-by-species.rds")

params
```

Build DO plots

```{r}
d <- list()
do_plots <- list()
for (i in seq_len(length(model_list))) {
  d[[i]] <- time_varying_density(model_list[[i]], predictor = "do_mlpl")
  if (length(d[[i]]) == 0) {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    do_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Dissolved O2", xlimits = c(0, 8)) + ggtitle(paste(species, names(model_list[i])))
  }
}
print(do_plots)
```

Build Temperature plots

```{r}
d <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  d[[i]] <- time_varying_density(temp_model_list[[i]], predictor = "temp")

  if (length(d[[i]]) == 0) {
    temp_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    temp_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Temperature", xlimits = c(2, 10)) +
      ggtitle(paste(species, names(temp_model_list[i])))
  }
}
print(temp_plots)
```

@@

Load Depth models
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- FALSE
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

@@

Build depth plots
```{r}
d <- list()
depth_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  d[[i]] <- time_varying_density(depth_model_list[[i]], predictor = "depth")

  if (length(d[[i]]) == 0) {
    depth_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } else {
    d[[i]]$x <- exp(d[[i]]$x)
    depth_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Depth", xlimits = c(0, 1000)) +
      ggtitle(paste(species, names(depth_model_list[i])))
  }
}
print(depth_plots)
```

```{r}
png(
  file = paste0(
    "figs/", spp,
    "/depth-", spp, covs, "-priors-", priors, ".png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = depth_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Plot time-varying effect of trawling at mean depth

```{r}
trawl_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  r <- depth_model_list[[i]]$tmb_obj$report()
  b3 <- r$b_rw_t[, 3]
  yrs <- sort(unique(depth_model_list[[i]]$data$year))
  b_j <- depth_model_list[[i]]$model$par[1:length(yrs)]

  SE <- 0.35 # Place-holder

@@

trawled <- data.frame(year = yrs, intercept = b_j, trawling = b3)
```
